Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-10-27 update-10-22/update-10-22.tex
Covid progression graph with sources

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{natbib}
\usepackage{pgfplots}

@@

	\begin{figure}[h]
		\centering
		\input{chicago-data}
		\label{fig:data}
		\caption{no}
	\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{chicago-spatial-covid-draft}

>>>>

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}

@@

	\begin{figure}[h]
		\centering
		\includegraphics[height=12cm]{chicago-data}
		\label{fig:data}
		\caption{Timeline of the progression of COVID-19 in Chicago with key public policy events marked.
			The COVID-19 data was obtained from the City of Chicago Data Portal \cite{Chicago-cases}.
			The dates of the policy events were gathered from the Illinois.gov press releases \cite{phase-5}, \cite{mask-lift}, \cite{full-vax}, \cite{start-vax}, \cite{phase-4}, the Chicago Tribune \cite{phase-3}, NBC Chicago \cite{phase-2}}
	\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{update-10-22}
